\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-10 manuscript.Rmd
All Demographics tables are no readable

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
appendix:
  - "appendix-1.Rmd"
mainfont: Arial
---

@@

```{r demographics, warning=F, message=F}
desc_kable %>% 
  kable_styling(latex_options = c("scale_down")) 
```

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header.tex
appendix:
  - "appendix-1.Rmd"
mainfont: Arial
---

@@

```{r demographics, warning=F, message=F}
desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
